Last glacial cycle glacier erosion potential in the Alps

### 2021-01-06 articles/erosion/alps-erosion.tex
Draft the results part. Unsure about this outline.

    Modelled cumulative erosion potential vary by several orders of magnitude.
    There is a very strong localization in valleys with a large catchment and
    valley heads, where the results are limited by model resolution.

    Fig.~\ref{fig:cumulative} -- Cumulative erosion.

@@

    Above a certain level of glaciation, erosion rates appear uncorrelated with
    the ice volume. Volumetric erosion rates during MIS~4 and MIS~2 are not
    higher than other parts of the last glacial cycle. However, there is a
    tendency for higher erosion rate during periods of ice retreat.

    Fig.~\ref{fig:evolution} -- Erosion rate and ice volume.

    Along the Rhine Glacier transect, stages of extensive glaciation see
    erosion rates localized in the lower part of the catchment. Erosion rates
    propagate inward during periods of ice retreat.

    Fig.~\ref{fig:transects} -- Erosion rate along transects.

    These results can be generalized to the entire model domain by using
    elevation as a proxy for along-flow distance. During periods of larger
    extent, erosion rates shift to lower elevation, leaving upper grounds
    untouched. During deglaciation, erosion propagates inland.

    Fig.~\ref{fig:hypsogram} -- Erosion rate and elevation.

>>>>

    The modelled cumulative (time-integrated) glacial erosion potential
    (Fig.~\ref{fig:cumulative}a) varies by several orders of magnitude
    from insignificant to (unrealistic, see below) kilometre-scale erosion
    potential. Its spatial patterns of modelled erosion potential show a very
    strong localization along the Alpine valleys, with local maxima at
    the Alpine gates where ice flow transited from valley to piedmont glaciers,
    and sometimes further up-valley.
    There is a genereral tendency for higher cumulative erosion in the
    north-western Alps where the input winter precipitation
    \citep[WorldClim,][Fig.~1h]{Seguinot.etal.2018} is higher and the
    preexisting glacial topography more pronounced.

@@

    The modelled volumic (domain-integrated) glacial erosion rates
    (Fig.~\ref{fig:cumulative}b) do not correlate with the modelled total ice
    volume. A comparison between the modelled ice volume and the modelled
    volumic erosion rate show no relation between these two quantities, except
    for the onset and termination of the glacial cycle were ice volume is low
    and sliding processes unlikely to be captured by the model resolution.
    Instead, erosion is modelled to be higher by a factor 3 to 10 during
    periods of glacier retreat, than during periods of glacier advance
    (Fig.~\ref{fig:evolution}).

% -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -
\subsection{Spatial migration}
% -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -

    A closer look at the Rhine Glacier, one of the paleo-ice sheet's largest
    outlets, reveals a spatial migration of the modelled high erosion rates.
    During glacier advance and stages of extensive glaciation, the modelled
    erosion rates are moderate and restricted to low elevations, while the
    most interior parts of the Alps \citep[modelled to be
    largely-cold-based][Fig.~6c]{Seguinot.etal.2018}, experience insignificant
    erosion rates (Fig.~\ref{fig:transects}a and~d). The modelled erosion
    rates both increase and propagate inwards during periods of glacier
    retreat (Fig.~\ref{fig:transects}b, c and~d).

    These results can be generalized to the entire model domain by using
    (present-day) bedrock altitude as a proxy for along-flow distance
    (Fig.~\ref{fig:hypsogram}). Periods of modelled increasing and maximum ice
    volume corresponds to local modelled erosion rate minima, with significant
    erosion rates restricted to lower elevations. On the other hand, periods of
    modelled decreased ice volume (and area) correspond to higher local
    modelled erosion rates and a shift of significant erosion rates to
    higher-elevation areas (Fig.~\ref{fig:hypsogram}).

    \note{I suddenly realize it may be better to highlight results from the
          Koppes et al. erosion law for tidewater glaciers instead, and maybe
          pull the sensitivity study up before the main results. To dedice
          about this I will need to get back to the Koppes and Cook paper to
          really understand what these laws are about.}
